\sysfull

### 2018-04-17 paper/systemdescription.tex

The programmer compiles their task-based code, and links to the \sys runtime, producing a \sys-enabled binary. The \sys runtime implements \sys's task-based programming and execution model. The runtime system also includes \sys's novel {\em virtualizing memory manager} and its {\em task coalescing manager}, and {\em task downscaling manager}, both of which are essential to \sys's adaptive task-based execution.

\textbf{\sys Task Coalescing Manager.} \sys relies on its task coalescing manager to dynamically {\em coalesce} statically\hyp{}defined tasks to avoid inessential overheads associated with completing tasks. By default, tasks run in a sequence and each task commits its task-shared state as it completes. The time and energy cost of a task's commit is unnecessary if the task and its successor both complete without a power failure. The key insight that \sys leverages is that the first task could have deferred its commit to the second task. {\em Coalescing} tasks by deferring the first commit avoids the fixed cost of the first commit (task transitioning overheads). Coalescing also amortizes per-variable commit cost, committing each location accessed by both tasks only after the second task, rather than once per task.

\sys's coalescing manager is an \emph{energy-aware} and \emph{software-based only} manager in a sense it uses the recent execution history as a metric to estimate the amount of the available energy to set the adequate coalesced task size accordingly. This fundamental feature prevents \sys from blind coalesced task adaptation which may result in a repeated power failure problem. For example, If \sys enlarges the coalesced task size by $x$ static tasks on a coalesced task completion and reduces it by the same number of static tasks on a power reboot, then \sys may need to reboot, for instance, ten times to reduce a coalesced task size from ten to one, when $x=1$. Details of coalescing will be given in Section~\ref{sec:task_coalescing}.

\textbf{\sys Task Downscaling Manager.} \sys's task downscaling manager is responsible for preserving the forward progress when \sys repeatedly fails on a single static task. The downscaling manager utilizes a timer-based technique and relies on the virtual memory manager to gain a full \emph{flexibility} on where to split a task. These features distinguish \sys task splitting technique from the traditional checkpointing. A checkpointing system that uses voltage threshold to place a checkpoint might cause a program to crash if the checkpoint happened to be placed between a peripheral initialization and its call. If a programmer disables interrupts between the peripheral initialization and the call, the program may fail indefinitely to progress since the checkpoint may only be deferred. The \sys task downscaling manager, on the other hand, triggers a \emph{partial commit} faster than the previous one on a repeated failure to guarantee forward progress. Details of task downscaling will be given in Section~\ref{sec:task_downsizing}.

\textbf{\sys Virtual Memory Manager.} \sys is able to efficiently coalesce tasks because of its efficient virtual memory manager. \sys's memory manager paginates memory and ensures that data in a page remain consistent despite power interruptions. \sys allows a task to manipulate data in a volatile copy of a page only. Pages swap between volatile and non-volatile memory, depending on the capacity of the volatile memory and the program's access pattern. \sys tracks a task's memory accesses efficiently at page granularity (rather than using, e.g., costly word-granular tracking). When a task ends, each page it accessed commits from volatile memory (or from a non-volatile swap region for dirty pages) back to the non-volatile main memory. Pages efficiently, atomically commit using a two-phase commit procedure accelerated using hardware support for direct memory access (DMA). Details of Virtual Memory Manager are will be given in Section~\ref{sec:memory_virtulaization}.

>>>>

The programmer compiles their task-based code, and links to the \sys runtime,
producing a \sys-enabled binary. The \sys runtime implements \sys's task-based
programming and execution model. The runtime system also includes \sys's novel
{\em virtualizing memory manager} and its {\em adaptive task scheduler}, both
of which are essential to \sys's adaptive task-based execution.

\textbf{\sys Adaptive Task Scheduler.} 
\sys's adaptive task scheduler decides when to coalesce consecutive tasks
together to amortize commit and transition costs, and when to downscale a task,
breaking it into multiple tasks, to avoid non-termination.

\sys's scheduler dynamically {\em coalesces} statically\hyp{}defined tasks to
avoid inessential overheads associated with completing tasks. By default, tasks
run in a sequence and each task commits its task-shared state as it completes.
The time and energy cost of a task's commit is unnecessary if the task and its
successor both complete without a power failure. The key insight that \sys
leverages is that the first task could have deferred its commit to the second
task. {\em Coalescing} tasks by deferring the first commit avoids the fixed
cost of the first commit (task transitioning overheads). Coalescing also
amortizes per-variable commit cost, committing each location accessed by both
tasks only after the second task, rather than once per task.  \sys makes
\emph{energy-aware} scheduling decisions, using a short history of recently
executed tasks to estimate available energy and guide future decisions. \sys
relies on {\em software only}, avoiding the need for additional circuitry to,
e.g., measure available energy.

%to set the adequate coalesced task
%size accordingly. This fundamental feature prevents \sys from blind coalesced
%task adaptation which may result in a repeated power failure problem. For
%example, If \sys enlarges the coalesced task size by $x$ static tasks on a
%coalesced task completion and reduces it by the same number of static tasks on
%a power reboot, then \sys may need to reboot, for instance, ten times to reduce
%a coalesced task size from ten to one, when $x=1$. Details of coalescing will
%be given in Section~\ref{sec:task_coalescing}.

\sys's scheduler {\em downscales} a task to preserve forward progress when a
single task repeatedly fails to execute to completion.  For a repeatedly-failing
task, the scheduler uses a timer that fires at a decreasing interval to
determine where to execute a {\em partial commit} of the task. Partial
commit saves progress through a task that runs for too long to complete
using the device's buffered energy. Eventually, after a series of partial
commits, the too-long task completes --- partial commit favors progress over task atomicity.  
When a task repeatedly fails, the scheduler uses a timer that counts an operating interval
that decreases in length with each failure and \sys partially commits at the end of the interval. 
Section~\ref{sec:task_coalescing} provides details of \sys's task scheduler.
%and relies on the virtual memory manager to gain a full \emph{flexibility} on
%where to split a task. These features distinguish \sys task splitting technique
%from the traditional checkpointing. A checkpointing system that uses voltage
%threshold to place a checkpoint might cause a program to crash if the
%checkpoint happened to be placed between a peripheral initialization and its
%call. If a programmer disables interrupts between the peripheral initialization
%and the call, the program may fail indefinitely to progress since the
%checkpoint may only be deferred. The \sys task downscaling manager, on the
%other hand, triggers a \emph{partial commit} faster than the previous one on a
%repeated failure to guarantee forward progress. Details of task downscaling
%will be given in Section~\ref{sec:task_downsizing}.

\textbf{\sys Virtual Memory Manager.} \sys is able to efficiently coalesce
tasks because of its efficient virtual memory manager. \sys's memory manager
paginates memory and ensures that data in a page remain consistent despite
power interruptions. \sys allows a task to manipulate data in a volatile copy
of a page only. Pages swap between volatile and non-volatile memory, depending
on the capacity of the volatile memory and the program's access pattern. \sys
tracks a task's memory accesses efficiently at page granularity (rather than
using, e.g., costly word-granular tracking). When a task ends, each page it
accessed commits from volatile memory (or from a non-volatile swap region for
dirty pages) back to the non-volatile main memory. Pages efficiently,
atomically commit using a two-phase commit procedure accelerated using hardware
support for direct memory access (DMA). Section~\ref{sec:memory_virtualization}
provides details of \sys's memory manager.
